\section{Official-Method Real-Feature Receipts}

\begingroup\raggedright
The real-feature preregistration digest is
\texttt{362065c8f110fd3eb096a638e12031ef}\allowbreak
\texttt{494eb208524c69216910307033dd7ed3}. The complete manifest digest is
\texttt{773ba872cab2b404900652a3d8f8f522}\allowbreak
\texttt{e9e29295df2d50bd2736d109e7182b0b}; its independent replay digest is
\texttt{bbf30f5db4f466325063ef0edb8c282b}\allowbreak
\texttt{47916b287c9139b6595b8b14b86af4d6}. All seven locked gates pass: complete
execution, positive usefulness, empirical safety, support discipline, modality
coverage, claim discipline, and receipt replay.\par
\endgroup

The frontier contains 13 rows in a fixed order: identity; INLP ranks 1, 2, 4,
and 8; LEACE; R-LACE ranks 1 and 4; TaCo with 1, 2, 3, and 5 removed
components; and MANCE++. Every transformation calls a pinned official
implementation and records its repository, commit, entry point, and parameters.
There are no proxy rows. Each candidate has a separately fitted tokenizer, so
its simultaneous table receives $\delta/13$ before continuum channel selection.
Because the protocol predates the transform-exact amendment, these rows use the
capacity-transfer fallback. The official-method study therefore evaluates the
frontier and release protocol, while the paired synthetic study measures the
exact refinement itself.

\begin{table}[t]
\centering
\small
\setlength{\tabcolsep}{3.0pt}
\begin{tabular}{rllrr}
\hline
Seed & Selected & Cert. & Ext. error & Ext. adv. \\
\hline
100 & INLP rank 4 & .3124 & .1817 & .0451 \\
101 & R-LACE rank 4 & .3086 & .2030 & .0720 \\
102 & INLP rank 4 & .3259 & .2047 & .0843 \\
103 & INLP rank 1 & .2991 & .1954 & .0598 \\
104 & INLP rank 4 & .3160 & .1863 & .0456 \\
\hline
\end{tabular}
\caption{BiasBios selected rows; all are externally safe.}
\label{supp:tab:biasselections}
\end{table}

\begin{table}[t]
\centering
\small
\setlength{\tabcolsep}{4.0pt}
\begin{tabular}{rll}
\hline
Seed & Selected & Cert. error \\
\hline
100 & LEACE & .2702 \\
101 & LEACE & .2818 \\
102 & LEACE & .2773 \\
103 & LEACE & .2955 \\
104 & LEACE & .2853 \\
\hline
\end{tabular}
\caption{Camelyon17 selected rows. Every natural external diagnostic is
unestimable because a required source is absent.}
\label{supp:tab:camselections}
\end{table}

All 65 BiasBios candidate rows are certifiable and externally safe. By contrast,
all 195 rows across Waterbirds, CivilComments, and GaitPDB satisfy the privacy
threshold only with certified worst error above .49; the selected decision is
therefore abstention. Natural external evaluation finds zero safe candidates in
CivilComments and GaitPDB and one of 65 in Waterbirds. That Waterbirds row is a
useful conservative case: favorable external behavior does not retroactively
make an uncertified construction-table decision deployable.

Camelyon17 has 65 certifiable candidate rows and selects LEACE on every seed,
but every external row is missing a required source class. The external audit
distribution is therefore identical under arbitrarily different missing-source
laws, exactly matching the non-identifiability theorem. We count these five
model-conditional releases separately from the five externally estimable
BiasBios selections. Reporting ``zero false acceptances'' refers only to those
five estimable selections and is not promoted to a population-frequency claim.

\paragraph{Exploratory transform-exact replay.}
After confirmatory outcomes were known, we re-optimized the exact envelope on
all 325 stored token tables. Exact certified error is no larger on every row and
strictly smaller on 133, with a maximum reduction of 3.54 percentage points.
Candidate deployments increase from 130 to 132: INLP rank 4 on Waterbirds seeds
102 and 103 crosses the utility contract, and both selected releases pass the
natural external diagnostic. Exact selection therefore deploys on 12 of 25
jobs; all seven externally estimable selections are diagnostically safe, five
Camelyon17 selections remain unestimable, and the remaining 13 jobs abstain.
This analysis is post-outcome and exploratory, not a new confirmatory study.

\begingroup\raggedright
The analysis digest is
\texttt{ea45e4ed7c47691e1813fea40d36293e}\allowbreak
\texttt{295db03245c11f4485c339ae7778aeae}; its independent 325-optimization replay
has digest
\texttt{3f3afabf41d5e4ff0c28c5d21dd68813}\allowbreak
\texttt{af54c6b47ea2f0e9d478bd9bd92850ac} and zero mismatches.\par
\endgroup
