\section{Notation and Exact Support Functions}

For one task label, let $P=(p_1,\ldots,p_G)$ collect the conditional fine-token
laws and let $M\in\mathrm{Stoch}(K,L)$ be a source-blind release channel. For an
attacker assignment $a\in[G]^L$, define
\begin{equation}
 v_{M,a,s}(c)=\sum_{z=1}^{L}M(c,z)\mathbf 1\{a(z)=s\}.
 \label{supp:eq:v}
\end{equation}
Every $v_{M,a,s}$ lies in $[0,1]^K$. The balanced Bayes accuracy has the two
equivalent forms
\begin{equation}
 \begin{aligned}
 A(P,M)&=\frac{1}{G}\sum_z\max_s(p_sM)(z)\\
 &=\frac{1}{G}\max_{a\in[G]^L}\sum_sp_s^\top v_{M,a,s}.
 \end{aligned}
 \label{supp:eq:bayes}
\end{equation}
The second identity follows because a finite-alphabet Bayes rule can be chosen
deterministically at each released token.

For empirical law $\widehat p$, radius $\epsilon$, and bounded score $v$, the
confidence-set support function is
\begin{equation}
 \Phi(\widehat p,\epsilon;v)=
 \max_{p\geq0,\,\mathbf 1^\top p=1,\,
 \|p-\widehat p\|_1\leq\epsilon}p^\top v.
 \label{supp:eq:support}
\end{equation}
Introducing positive and negative displacement variables gives a linear
program. Its compact dual is
\begin{align}
 \min_{\nu,\lambda,\theta}\quad
 &\nu+\widehat p^\top\theta+\epsilon\lambda,\\
 \text{s.t.}\quad
 &\nu+\theta_c\geq v_c\quad\forall c,\\
 &-\lambda\leq\theta_c\leq\lambda\quad\forall c,
 \qquad \lambda\geq0.
 \label{supp:eq:supportdual}
\end{align}
Strong duality holds because the primal confidence set is nonempty and compact.
The implementation also evaluates Eq.~\eqref{supp:eq:support} independently by
moving at most $\epsilon/2$ probability mass from low-score to high-score
coordinates, respecting simplex boundaries.

\section{Adaptive Confidence Envelope}

Let $\mathcal C_s=\{p\in\Delta_K:
\|p-\widehat p_s\|_1\leq\epsilon_s\}$ and define
\begin{equation}
 \overline A(\widehat P,M)=\frac{1}{G}
 \max_{a\in[G]^L}\sum_s
 \Phi(\widehat p_s,\epsilon_s;v_{M,a,s}).
 \label{supp:eq:abar}
\end{equation}

\begin{theorem}[Exact adaptive universal-attacker envelope]
On the event $\mathcal E=\{p_s\in\mathcal C_s\ \forall s,y\}$,
$A(P,M)\leq\overline A(\widehat P,M)$ simultaneously for every stochastic
release channel $M$, including one selected from the same table. For fixed
$M$, $\overline A$ is the exact supremum of $A(P,M)$ over
$\mathcal C_1\times\cdots\times\mathcal C_G$.
\end{theorem}

\begin{proof}
Using Eq.~\eqref{supp:eq:bayes}, take the supremum over the product confidence
set. The assignment family is finite, so the supremum and assignment maximum
commute. For a fixed assignment, the objective is additive in sources and the
confidence set is a Cartesian product, so each source maximization separates
and equals the support function in Eq.~\eqref{supp:eq:support}. This proves
exactness for every fixed $M$. On $\mathcal E$, the true law is one feasible
point in every confidence set, giving the upper bound. The statement is
pointwise over the complete channel space, so it remains true after any
measurable same-table selection of $M$.
\end{proof}

For positive stratum count $n_{s,y}$ and fixed allocation $\delta_{s,y}$, the
confirmation uses
\begin{equation}
 \epsilon_{s,y}=\min\left\{2,
 \sqrt{\frac{2\log((2^K-2)/\delta_{s,y})}{n_{s,y}}}\right\}.
 \label{supp:eq:weissman}
\end{equation}
A union bound gives $\Pr(\mathcal E)\geq1-\sum_{s,y}\delta_{s,y}$. A zero-count
stratum receives radius two and is covered deterministically.

\section{Channel Capacity and Common-Shift Transfer}

Define
\begin{equation}
 \operatorname{Cap}_G(M)=\frac{1}{G}
 \max_{a\in[G]^L}\sum_s\max_c v_{M,a,s}(c).
 \label{supp:eq:cap}
\end{equation}

\begin{lemma}[Exact arbitrary-shift capacity]
$\operatorname{Cap}_G(M)=\sup_{r_1,\ldots,r_G\in\Delta_K}A(R,M)$.
\end{lemma}

\begin{proof}
Expand $A(R,M)$ by Eq.~\eqref{supp:eq:bayes}. For fixed assignment $a$, each
source law $r_s$ can concentrate all mass on a token maximizing
$v_{M,a,s}(c)$. The source suprema separate and the finite maxima commute,
yielding Eq.~\eqref{supp:eq:cap}.
\end{proof}

For two sources, uniform-prior Bayes accuracy is
$(1+\operatorname{TV}(r_1M,r_2M))/2$. The diameter of the convex hull of channel
rows is attained by two rows, hence
$2\operatorname{Cap}_2(M)-1=max_{c,c'}
\operatorname{TV}(M(c,\cdot),M(c',\cdot))$, the Dobrushin coefficient.

For common pre-release channel $T$, define
\begin{equation}
 \rho_T(M)=\max_c\operatorname{TV}((TM)(c,\cdot),M(c,\cdot)).
 \label{supp:eq:rho}
\end{equation}

\begin{lemma}[Approximate invariance transfer]
For every source experiment $P$,
\begin{equation}
 A(P,TM)\leq
 \min\{\operatorname{Cap}_G(M),A(P,M)+\rho_T(M)\}.
 \label{supp:eq:transfer}
\end{equation}
\end{lemma}

\begin{proof}
For source $s$, convexity of total variation gives
$\operatorname{TV}(p_sTM,p_sM)\leq
\sum_cp_s(c)\operatorname{TV}((TM)(c,\cdot),M(c,\cdot))\leq\rho_T(M)$.
The success probability of any attacker changes by at most this distance.
Averaging over sources and maximizing the attacker gives the additive bound.
The capacity bound follows by treating $p_sT$ as an arbitrary fine-token law
and applying the preceding lemma.
\end{proof}

\section{Structured External Shift}

For label $y$, suppose
\begin{equation}
 q_s=t_yp_sT_y+(1-t_y)r_s,
 \qquad t_y\geq1-\eta_y,
 \label{supp:eq:model}
\end{equation}
with common $T_y\in\mathcal T_y$ and common retained mass $t_y$ across sources.
For a polytope with finite extremes
$\mathcal V_y=\operatorname{ext}(\mathcal T_y)$, define
\begin{equation}
 \begin{aligned}
 \overline A_y^X(M)
 &=\frac1G\max_{T\in\mathcal V_y,\,a\in[G]^L}\sum_s\Big[
 \\[-2pt]&\quad (1-\eta_y)
 \Phi(\widehat p_{s,y},\epsilon_{s,y};Tv_{M,a,s})
 \\[-2pt]&\quad +\eta_y\max_cv_{M,a,s}(c)\Big].
 \end{aligned}
 \label{supp:eq:exactconfidence}
\end{equation}

\begin{theorem}[Transform-exact post-selection certificate]
On $\mathcal E$, simultaneously for every selected $M$ and every external law
in Eq.~\eqref{supp:eq:model}, $A(Q,M)\leq\overline A_y^X(M)$. For fixed $M$,
the right-hand side is the exact supremum over the product confidence sets,
transform polytope, allowed retained masses, and residual laws.
\end{theorem}

\begin{proof}
Expand balanced Bayes accuracy using Eq.~\eqref{supp:eq:bayes}. For fixed
$T,t$, and attacker assignment, the source confidence sets and residual
simplexes separate. Their support values are
$\Phi(\widehat p_{s,y},\epsilon_{s,y};Tv_{M,a,s})$ and
$\max_cv_{M,a,s}(c)$. The latter is no smaller because every coordinate of
$Tv$ is a convex combination of coordinates of $v$. The maximizing retained
mass is therefore $t=1-\eta_y$. The resulting confidence support is convex in
$T$, so its maximum over a polytope is attained at an extreme. All remaining
maxima are finite and commute. This gives exactness for fixed $M$; pointwise
coverage over all channels preserves the bound after same-table selection.
\end{proof}

For a transform family that cannot be enumerated, let
$B_y(M)=\min\{\operatorname{Cap}_G(M),
\overline A_y(\widehat P,M)+\rho_{\mathcal T_y}(M)\}$.

\begin{corollary}[Capacity-transfer fallback]
On $\mathcal E$,
\begin{equation}
 A(Q,M)\leq(1-\eta_y)B_y(M)
 +\eta_y\operatorname{Cap}_G(M).
 \label{supp:eq:shiftbound}
\end{equation}
\end{corollary}

\begin{proof}
The retained experiment is bounded by Eq.~\eqref{supp:eq:transfer}, the
adaptive envelope bounds its unknown reference term, and residuals are bounded
by capacity. Since $B_y(M)\leq\operatorname{Cap}_G(M)$, the largest value over
$t_y\geq1-\eta_y$ occurs at $t_y=1-\eta_y$.
\end{proof}

The exact confidence envelope is no larger than this fallback because it is
the supremum over the same set. At zero confidence radius, it becomes the
known-population external risk
\begin{equation}
 \begin{aligned}
 \frac{1}{G}\max_{T\in\operatorname{ext}(\mathcal T_y),\,a\in[G]^L}
 \sum_s\big[&(1-\eta_y)p_{s,y}^\top T v_{M,a,s}\\
 &+\eta_y\max_cv_{M,a,s}(c)\big].
 \end{aligned}
 \label{supp:eq:exactprivacy}
\end{equation}
used by the separately implemented synthetic evaluator.

\section{Utility Certificate}

Fix decoder $g:[L]\to[J]$, let
$\ell_y(z)=\mathbf 1\{g(z)\neq y\}$, and write
$u_y=M\ell_y$. Define
\begin{align}
 \overline E_{s,y}(M,g)&=
 \Phi(\widehat p_{s,y},\epsilon_{s,y};u_y),\\
 \kappa_y(M,g)&=\sup_{T\in\mathcal T_y}
 \max\{0,\max_c((TM-M)\ell_y)(c)\},\\
 U_y(M,g)&=\max_cu_y(c).
\end{align}

Define the transform-exact value
\begin{equation}
 \begin{aligned}
 \overline E^X_{s,y}(M,g)
 &=\max_{T\in\mathcal V_y}\Big[(1-\eta_y)
 \\[-2pt]&\quad\Phi(\widehat p_{s,y},\epsilon_{s,y};Tu_y)
 +\eta_y\max_cu_y(c)\Big].
 \end{aligned}
 \label{supp:eq:exactutilityconfidence}
\end{equation}

\begin{corollary}[Transform-exact adaptive utility certificate]
On $\mathcal E$, every selected $(M,g)$ satisfies
$\operatorname{Err}_{s,y}(Q,M,g)\leq\overline E^X_{s,y}(M,g)$, and the
right-hand side is exact over the stated confidence ball and shift class.
\end{corollary}

\begin{proof}
Repeat the transform-exact proof for bounded loss $\ell_y$, without averaging
over sources or maximizing an attacker assignment.
\end{proof}

The capacity-transfer fallback is
\begin{corollary}[Adaptive shifted-utility fallback]
On $\mathcal E$, every selected $(M,g)$ satisfies
\begin{equation}
 \operatorname{Err}_{s,y}(Q,M,g)\leq
 (1-\eta_y)D_{s,y}(M,g)+\eta_yU_y(M,g),
 \label{supp:eq:utility}
\end{equation}
where
$D_{s,y}=\min\{U_y,\overline E_{s,y}+\kappa_y\}$.
\end{corollary}

\begin{proof}
Apply the structured-shift proof to the bounded loss $\ell_y$. The common
component differs from its reference expectation by at most the largest
positive directional defect $\kappa_y$, while the arbitrary residual
concentrates on a row with maximal error $U_y$.
\end{proof}

The transform-exact utility value is never larger than this fallback.

The exact population utility risk used in the independent evaluator is
\begin{equation}
 \max_{T\in\operatorname{ext}(\mathcal T_y)}
 \left[(1-\eta_y)p_{s,y}^\top TM\ell_y
 +\eta_y\max_c(M\ell_y)(c)\right].
 \label{supp:eq:exactutility}
\end{equation}

\section{No-Free-Lunch Boundary}

\begin{theorem}[Unrestricted differential shift]
For $G\geq2$, $\operatorname{Cap}_G(M)=1/G$ if and only if all rows of $M$ are
identical.
\end{theorem}

\begin{proof}
Identical rows make every released source law identical. Conversely, if two
rows differ, choose two residual source laws concentrated on those rows and
place every remaining source on either row. The released source laws are not
all identical, so uniform-prior Bayes accuracy is strictly above chance.
Exactness of Eq.~\eqref{supp:eq:cap} completes the argument.
\end{proof}

For two fine tokens $c_0,c_1$ with different task labels, suppose a decoder has
row-wise errors at most $e_0,e_1$. The decoder decision event occurs with
probability at least $1-e_0$ under $M(c_0,\cdot)$ and at most $e_1$ under
$M(c_1,\cdot)$. Total variation is therefore at least $1-e_0-e_1$, giving
\begin{equation}
 2\operatorname{Cap}_2(M)-1\geq1-e_0-e_1.
 \label{supp:eq:utilitylower}
\end{equation}
Thus a nontrivial task contract is incompatible with chance-level source
capacity under unrestricted differential shift.

\section{Missing-Source Non-Identifiability}

Fix two required sources and a released-token law $q_0M$ for source zero.
Suppose an external audit contains no source-one rows, so its observed-data
distribution is identical for every $q_1\in\Delta_K$. Define
\begin{equation}
 A_{\rm miss}(q_0,M)=\sup_{q_1\in\Delta_K}A((q_0,q_1),M).
 \label{supp:eq:missing}
\end{equation}

\begin{theorem}[Missing-source non-identifiability]
Let a possibly randomized protocol observe no source-one rows and claim
$A((q_0,q_1),M)\leq\tau$. If its false-certification probability is at most
$\delta<1$ uniformly over every $q_1$, then for
$\tau<A_{\rm miss}(q_0,M)$ it can issue that claim with probability at most
$\delta$.
\end{theorem}

\begin{proof}
The finite-simplex supremum is attained; call a maximizer $q_1^*$. The audit's
observed-data distribution does not depend on the missing law. Consequently,
every event on which the protocol claims a bound below
$A((q_0,q_1^*),M)$ is a false-certification event under $q_1^*$, and uniform
validity limits that event to probability $\delta$.
\end{proof}

The same indistinguishability argument for a missing source--label utility
stratum replaces Eq.~\eqref{supp:eq:missing} by
$\max_c(M\ell_y)(c)$. These are precisely the full-simplex terms used when a
stratum has count zero. Moreover, if $M$ is nonconstant, then
$A_{\rm miss}(q_0,M)>1/2$ for every $q_0$: the mixture $q_0M$ cannot equal every
nonidentical channel row, and a missing source concentrated on a differing row
has positive total-variation distinguishability. Missing required strata must
therefore be reported as unestimable unless an external structural assumption
identifies their laws.

\section{Abstention Theory}

Let $V(P,e)$ be the globally optimal certified worst conditional error for
confidence balls centered at $P$ with common radius $e$. With deployed radius
$e_n$, define
$r_n^*=\sup\{r\geq0:V(P,e_n+r)\leq\tau_U\}$.

\begin{proposition}[Finite-sample abstention envelope]
For $H$ registered strata of size $n$,
\begin{equation}
 \Pr(\text{MOSAIC abstains})\leq
 \min\{1,H(2^K-2)e^{-n(r_n^*)^2/2}\}.
 \label{supp:eq:abstain}
\end{equation}
\end{proposition}

\begin{proof}
If every empirical stratum is within distance $r$ of its population law, each
radius-$e_n$ ball around the empirical law is contained in the
radius-$(e_n+r)$ ball around the population law. A feasible population-centered
pair for the larger balls remains feasible for the empirical problem. Apply
the Weissman bound and a stratum union bound, then let $r$ approach $r_n^*$.
\end{proof}

For the preregistered local power curve, write $V_n(P)=V(P,e_n)$. Under local
uniqueness of the decoder and certificate branches together with strong
regularity of the resulting parametric linear program, the value is
differentiable. If $h_{n,s,y}$ is its simplex gradient and
$\Sigma_{s,y}=\operatorname{diag}(p_{s,y})-p_{s,y}p_{s,y}^\top$, the finite-$n$
delta-method prediction is
\begin{equation}
 \Phi_{\mathrm N}\!\left(
 \frac{\tau_U-V_n(P)}{
 \sqrt{n^{-1}\sum_{s,y}h_{n,s,y}^\top\Sigma_{s,y}h_{n,s,y}}}
 \right).
 \label{supp:eq:power}
\end{equation}
The locked analysis estimates each gradient by centered simplex-preserving
finite differences at step sizes $10^{-4}$ and $5\times10^{-5}$ and rejects the
approximation if their maximum discrepancy exceeds $5\times10^{-3}$.

\section{Optimization Certificate}

For fixed decoder, each support-function dual, transformed score, and residual
row maximum in Eqs.~\eqref{supp:eq:exactconfidence} and
\eqref{supp:eq:exactutilityconfidence} has a linear epigraph in the channel and
auxiliary variables. Enforcing all transform extremes and attacker assignments
therefore gives one linear program per decoder; enumerating all $J^L$ decoders
returns the global transform-exact finite-alphabet optimum. The
capacity-transfer fallback represents each minimum as a binary disjunction and
solves a mixed-integer linear program per decoder.

Globality is asserted only when every decoder and attacker assignment is
enumerated, the exact LP reports an optimal status or the fallback reports
numerical zero MIP gap, the primal residual is at most $2\times10^{-7}$, and an
independent implementation reproduces every certificate and the objective at
the same tolerance. A timeout, nonzero gap, oversized assignment family, or
post-hoc mismatch cannot return a deployment.

The exact audit checks zero-radius agreement with a separate population
evaluator, binary confidence-ball endpoints, 100 randomized dominance
comparisons with the fallback, and dense channel grids. The fallback audit
compares 30 randomized small instances with exhaustive $21^K$ grids and
includes a witness in which the best stochastic certified error is $0.371588$
while every deterministic release has certified error $1$.

\section{Locked Experimental Protocol}

The synthetic population has two labels, two sources, and three fine tokens.
For label zero the source laws are $(0.80,0.15,0.05)$ and
$(0.65,0.30,0.05)$; for label one they are $(0.05,0.20,0.75)$ and
$(0.05,0.35,0.60)$. The common-transform set is the convex hull of identity and
a nearest-neighbor smoothing channel. The hard safety scenario uses
$\eta=0.20$, privacy-advantage threshold $0.30$, and worst conditional error
threshold $0.40$. The retention scenario uses $\eta=0.10$, thresholds $0.35$
and $0.45$. Every source--label stratum contains exactly $n$ independent draws.

The confirmation fixes 1,000 replicates in each of three hard-scenario and five
retention-scenario sample-size cells. It compares eight rules and stores 64,000
method-level receipts. The preregistration fixes all seeds, methods, intervals,
and pass criteria, hashes the theorem and implementation, and was pushed before
the confirmation began. Pilot seeds zero through 199 are excluded. The oldest
aggregate-only pilot is retained as design history but cannot support a
channel-level claim; every later pilot row is replayed by the exact evaluator.

\input{mosaic_supplement_results}

\input{mosaic_transform_exact_supplement_results}

\input{mosaic_real_supplement_results}

\section{Reproducibility Manifest}

MOSAIC optimization, confirmations, and audits ran on an Apple M4 system with
10 CPU cores and 16 GB unified memory under macOS 26.2 (arm64). The locked
Python environment was Python 3.12.13 with NumPy 2.5.1, SciPy 1.18.0,
scikit-learn 1.9.0, PyTorch 2.13.0, and the HiGHS LP/MILP backend exposed by
SciPy. No GPU is
required once the registered feature stores have been constructed; synthetic
confirmation and every replay are CPU-only.

The named package reports the exact preregistration hash, Git commit, software
versions, and artifact hashes. The anonymous package retains the same internal
identifiers while replacing public authorship and repository metadata as
required by double-blind review. Raw synthetic receipts contain no private or
human-subject data. Real-domain experiments, if included, retain dataset terms,
official split definitions, preprocessing hashes, and method-specific code
provenance in a separate manifest.
