\section{Official-Method Feature Results}

All 25 dataset--seed jobs and all 325 registered candidate rows completed with
no proxy implementations or optimization failures. The independent replay
reconstructed every confidence radius, certificate, selected channel, decoder,
external diagnostic, and lexical tie break with zero mismatch. Table
\ref{tab:realfrontier} reports the complete selection behavior.

\begin{table*}[t]
\centering
\small
\setlength{\tabcolsep}{5.1pt}
\begin{tabular}{llclcl}
\hline
Dataset & Modality & Deploy & Selected family & Best cert. error & Natural external diagnostic \\
\hline
Waterbirds & vision & 0/5 & -- & .499 & 1/65 candidate rows safe; none certified \\
Camelyon17-WILDS & medical vision & 5/5 & LEACE (5) & .282 & unestimable: required source absent \\
CivilComments-WILDS & text & 0/5 & -- & .500 & 0/65 candidate rows safe \\
BiasBios-Clinical & clinical text & 5/5 & INLP (4), R-LACE (1) & .312 & 5/5 selections safe; 65/65 rows safe \\
GaitPDB & time series & 0/5 & -- & .500 & 0/65 candidate rows safe \\
\hline
\end{tabular}
\caption{Locked official-method frontier, five seeds per dataset and 13
candidates per seed. ``Best cert. error'' is the mean selected value for
deployment rows and the mean minimum available value for abstention rows.
External diagnostics are descriptive and do not establish structured-shift
membership.}
\label{tab:realfrontier}
\end{table*}

BiasBios provides the positive real-feature case. Every official candidate
clears both contracts on all five seeds; MOSAIC selects INLP four times and
R-LACE once. The selected mean certified worst error is .312 (range
.299--.326), while the natural external diagnostic has mean worst error .194
and mean source advantage .061. All five estimable selections are externally
safe, although five seeds are too few for a strong frequency claim.

An audited post-outcome exact replay improves 133 of 325 objectives and adds two
diagnostically safe Waterbirds deployments; it is exploratory and does not
establish shift-class membership.

The negative rows explain why an explicit release rule matters. Every candidate
in Waterbirds, CivilComments, and GaitPDB clears the privacy threshold only by
giving a certified worst error near .50, above the registered .49 utility
contract, so MOSAIC abstains on all 15 jobs. Natural external diagnostics agree
on CivilComments and GaitPDB; one of 65 Waterbirds candidates happens to be safe
externally but is not certifiable from its construction table. Conversely,
Camelyon17 produces five certifiable LEACE releases under the registered shift
model, but its natural external split lacks a required source class. The
missing-source theorem therefore forces the external result to be labeled
unestimable. Across the five externally estimable selected releases there are
zero false acceptances; this is a diagnostic check, not proof that the benchmark
splits satisfy Eq.~\eqref{eq:shift}.
