\section{Shift-Robust Paired Certification}
\label{app:shift-robust-theory}

Let $P$ denote the certification reference distribution and let
$V:\mathcal{X}\to[a,b]$
be a bounded audit variable.  In the target-preservation application,
$V=H_e$ is the paired increase in loss caused by edit $e$ relative to the
identity edit on the same example.  For $\Gamma\geq 1$, define the ambiguity
set
\begin{equation}
  \mathcal{Q}_{\Gamma}(P)=\left\{Q\ll P:
  0\leq \frac{\mathrm{d}Q}{\mathrm{d}P}\leq\Gamma
  \quad P\text{-almost surely}\right\}
\end{equation}
and the robust risk
$\rho_{\Gamma,P}(V)=\sup_{Q\in\mathcal{Q}_{\Gamma}(P)}\mathbb{E}_Q[V]$.
The reference law is contract-specific. Target contracts use the
environment-conditional law $P_g$. Leakage uses $P_s$, the law conditional on
represented source class $s\in\{0,1\}$, and evaluates equal-weight robust
class recall rather than ordinary accuracy. Accordingly, an admissible
deployment profile requires $Q_g\in\mathcal Q_{\gamma_g}(P_g)$ for target
harm and $Q_s\in\mathcal Q_{\eta_s}(P_s)$ for leakage. Environment mixture
weights may vary arbitrarily. Source-class prevalences may also vary
arbitrarily because the leakage estimand fixes the two class weights at one
half; this does not imply control of prevalence-weighted ordinary accuracy.

\begin{lemma}[Reweighting--CVaR identity]
\label{lem:cvar-identity}
For every bounded $V$ and $\Gamma\geq1$,
\begin{equation}
  \rho_{\Gamma,P}(V)
  =\inf_{\eta\in[a,b]}
  \left\{\eta+\Gamma\,\mathbb{E}_P[(V-\eta)_+]\right\}.
\end{equation}
Thus $\rho_{\Gamma,P}$ is upper-tail conditional value at risk at level
$1-1/\Gamma$.
\end{lemma}

\begin{proof}
Write $w=\mathrm{d}Q/\mathrm{d}P$.  The primal problem maximizes
$\mathbb{E}_P[wV]$ subject to $0\leq w\leq\Gamma$ and
$\mathbb{E}_P[w]=1$.  Introducing a multiplier $\eta$ for the equality
constraint and maximizing pointwise over $w$ gives
$\eta+\Gamma\mathbb{E}_P[(V-\eta)_+]$.  Strong duality follows because
$w\equiv1$ is feasible and the bounded linear program has a finite optimum.
The optimizer places the largest permitted mass on the upper tail of $V$.
\end{proof}

Given independent certification observations $V_1,\ldots,V_n$, let
$\widehat P_n$
be their empirical distribution and let
\begin{equation}
  \widehat\rho_{\Gamma,n}(V)
  =\inf_{\eta\in[a,b]}
  \left\{\eta+\frac{\Gamma}{n}\sum_{i=1}^n(V_i-\eta)_+\right\}.
\end{equation}

\paragraph{Probability space and protocol contract.}
Let $\mathcal F_0$ contain everything fixed before certification: the
construction data and randomness, the finite candidate edits, whether identity
is selectable, target probes, registered attackers, audit variables, required
environment and source cells, thresholds, confidence level, candidate utility
rule, and the ambiguity model and profile caps (but not the eventual profile
chosen inside a reported envelope). Conditional on
$\mathcal F_0$, certification examples are independent draws from the declared
reference law. Within a represented cell, their audit values are therefore
i.i.d. from its conditional law; validity may be conditioned on the realized
cell count. Candidates and components may share examples, and no independence
across candidates, environments, or attackers is assumed. Probability below is
over the certification draw and any protocol randomness not already included
in $\mathcal F_0$. The guarantees hold conditionally for every admissible
realization of $\mathcal F_0$ and hence also unconditionally by iterated
expectation. A candidate, attacker, threshold, or screening rule chosen using
certification outcomes is outside this contract unless its adaptivity is
explicitly covered by the confidence construction.

\begin{theorem}[Uniform robust paired-edit certificate]
\label{thm:robust-paired}
Fix $K$ bounded audit variables before observing their certification folds.
Variable $k$ has range $[a_k,b_k]$ and $n_k$ independent observations.  Define
\begin{equation}
\begin{aligned}
 \epsilon_k&=\sqrt{\frac{\log(2K/\delta)}{2n_k}},\\
 U_k(\Gamma)&=\min\left\{b_k,
 \widehat\rho_{\Gamma,n_k}(V_k)
 +\Gamma(b_k-a_k)\epsilon_k\right\}.
\end{aligned}
\end{equation}
Then, with probability at least $1-\delta$, simultaneously for all $k$ and
all $\Gamma\geq1$, and all $Q\in\mathcal{Q}_{\Gamma}(P_k)$,
$\mathbb{E}_Q[V_k]\leq U_k(\Gamma)$.
Consequently, any data-dependent edit selected only when its paired target-harm
bound is at most $\tau$ and all of its preregistered attacker-leakage bounds
are at most $\lambda$ satisfies those contracts for every allowed deployment
distribution.
\end{theorem}

\begin{proof}
For one variable, the Dvoretzky--Kiefer--Wolfowitz inequality gives
$\sup_t|F_n(t)-F(t)|\leq\epsilon_k$ except on an event of probability
$\delta/K$.  For every $\eta\in[a_k,b_k]$,
\begin{align}
 &\left|\mathbb{E}_P[(V-\eta)_+]
 -\mathbb{E}_{\widehat P_n}[(V-\eta)_+]\right| \nonumber\\
 &\quad=\left|\int_{\eta}^{b_k}(F_n(t)-F(t))\,\mathrm{d}t\right| \nonumber\\
 &\quad\leq(b_k-a_k)\epsilon_k.
\end{align}
Applying this inequality inside Lemma~\ref{lem:cvar-identity} and taking the
infimum over $\eta$ yields
$\rho_{\Gamma,P}(V)\leq\widehat\rho_{\Gamma,n}(V)
+\Gamma(b_k-a_k)\epsilon_k$.  A union bound over $K$ audit variables proves
simultaneous validity.  On this event, every accepted edit obeys each contract;
selection among accepted edits does not change the event.
\end{proof}

\begin{corollary}[Exact discrete paired certificate]
\label{cor:exact-discrete}
Let $L\in\{0,1\}$ have success probability $p$, and let
$H\in\{-1,0,1\}$ have probabilities $(p_-,p_0,p_+)$. Then
\begin{equation}
 \rho_{\Gamma,P}(L)=\min\{1,\Gamma p\},
\end{equation}
and, writing $a=\Gamma p_+$ and $d=\Gamma(1-p_-)$,
\begin{equation}
 \rho_{\Gamma,P}(H)=
 \begin{cases}
  1, & a\geq1,\\
  a, & a<1\leq d,\\
  a+d-1, & d<1.
 \end{cases}
\end{equation}
For a registered family of $K$ contracts, replace $p$ by a one-sided
Clopper--Pearson upper bound at error $\delta/K$. For paired harm, let
$U_+$ be a one-sided upper bound for $p_+$ and $L_-$ a one-sided lower bound
for $p_-$, each at error $\delta/(2K)$, and substitute
$\widetilde p_+=\min\{U_+,1-L_-\}$ and $\widetilde p_-=L_-$ in the formula.
The clipping preserves the probability-simplex constraint and can only tighten
the upper bound. These substitutions give simultaneous upper confidence curves
for every $\Gamma\geq1$. Inverting the curves therefore gives the same
shift-radius and false-acceptance guarantees as
Theorem~\ref{thm:shift-radius}.
\end{corollary}

\begin{proof}
The worst density ratio assigns weight $\Gamma$ first to value one, then to
value zero, and finally assigns the residual unit mass to value minus one.
This greedy allocation yields the displayed formulas. The Bernoulli expression
is increasing in $p$. The paired expression is increasing in $p_+$ and
decreasing in $p_-$ in every branch. On the joint confidence event,
$p_+\leq U_+$ and $p_-\geq L_-$. Since also $p_+\leq1-p_-\leq1-L_-$,
$p_+\leq\widetilde p_+$; hence the clipped substitution dominates the true
robust risk. A union bound gives simultaneous validity. The coverage event is
independent of $\Gamma$, so it holds over the entire continuum and remains
valid after inversion and edit selection.
\end{proof}

For attacker $a$, let $L_{e,a}=\mathbf 1\{a_e(Z^e)=S\}$ and define the
balanced robust leakage
\begin{equation}
 B_{e,a}(\eta_0,\eta_1)
 =\frac12\sum_{s\in\{0,1\}}\rho_{\eta_s,P_s}(L_{e,a}).
 \label{eq:balanced-leakage}
\end{equation}
If $U_{e,a,s}(\eta_s)$ is an upper confidence curve for the class-$s$
recall, then
$\widehat B_{e,a}=\tfrac12(U_{e,a,0}+U_{e,a,1})$ upper-bounds
Eq.~\eqref{eq:balanced-leakage} on the intersection of the two coverage
events. A component-level error budget $\alpha$ is therefore obtained by
using one-sided Clopper--Pearson bounds at $\alpha/2$ for the two recalls.

\begin{lemma}[Source-prior invariance]
\label{prop:source-prior}
Let the deployment model declare both source-conditional laws and let source
prevalence be any $\pi\in[0,1]$, including $0$ or $1$. Suppose the two
source-conditional deployment laws obey
$Q_s\in\mathcal Q_{\eta_s}(P_s)$. The balanced robust leakage in
Eq.~\eqref{eq:balanced-leakage} is independent of $\pi$ and is at most
$\lambda$ whenever $\widehat B_{e,a}\leq\lambda$. A constant binary attacker
has balanced leakage $1/2$ at $\eta_0=\eta_1=1$, regardless of which class it
always predicts.
\end{lemma}

\begin{proof}
The estimand assigns weight one half to each conditional recall by definition,
so prevalence $\pi$ does not enter it. On the joint confidence event, each
robust recall is at most its corresponding upper curve; averaging gives the
first claim. A constant attacker has class recalls $(1,0)$ or $(0,1)$ under
IID evaluation, whose equal-weight mean is $1/2$.
At $\pi\in\{0,1\}$, the unused conditional remains part of the declared
standardization model; the balanced functional is not ordinary accuracy
observable from a deployment sample containing only one class.
\end{proof}

\begin{theorem}[Fixed-profile candidate intersection--union test]
\label{thm:iut}
Fix $M$ candidate edits before certification. For candidate $e$, let
$\{R_{e,j}\leq c_j\}_{j\in\mathcal J_e}$ contain every target and balanced
leakage component at one declared shift profile. Suppose each reported
component bound $U_{e,j}$ undercovers $R_{e,j}$ with probability at most
$\alpha=\delta/M$. For paired target harm, the positive- and negative-count
bounds split this $\alpha$ equally; for balanced leakage, its two class-recall
bounds do the same. Accept candidate $e$ only if
$U_{e,j}\leq c_j$ for every $j$, then select any accepted candidate by a
prespecified measurable utility rule, which may use certification values. The
probability of deploying any candidate that violates at least one component
contract is at most $\delta$.
If identity is itself a selectable deployment action, it is included among the
$M$ candidates; using identity only to define paired harm does not add a
selection hypothesis.
\end{theorem}

\begin{proof}
For each unsafe candidate $e$, choose one population-violated component
$j(e)$ before the certification draw. False acceptance of $e$ implies
$U_{e,j(e)}\leq c_{j(e)}<R_{e,j(e)}$, an undercoverage event of probability at
most $\alpha$. No union bound across components is needed because acceptance
requires every component to pass: this is an intersection--union test. A union
bound over the at most $M$ unsafe candidates gives $M\alpha=\delta$.
Selection among accepted candidates is contained in the same event.
\end{proof}

\begin{corollary}[Worst-group mixture shift]
\label{cor:mixture}
Let $P_g$ be certified group-conditional reference distributions for
$g\in\mathcal{G}$. If
$\rho_{\Gamma,P_g}(V_e)\leq c$ is simultaneously certified for every edit
$e$ and group $g$, then for every collection
$Q_g\in\mathcal{Q}_{\Gamma}(P_g)$ and every deployment mixture
$Q_{\pi}=\sum_g\pi_gQ_g$ with $\pi$ in the probability simplex,
$\mathbb{E}_{Q_{\pi}}[V_e]\leq c$.
\end{corollary}

\begin{proof}
$\mathbb{E}_{Q_{\pi}}[V_e]=\sum_g\pi_g\mathbb{E}_{Q_g}[V_e]\leq
\sum_g\pi_gc=c$.
\end{proof}

Let $U^T_{e,g}(\gamma_g)$ be a simultaneous upper curve for paired target harm
in observed environment $g$, and let $U^L_{e,a,s}(\eta_s)$ be one for attacker
$a$'s class-$s$ recall. The \emph{support-aware representation-edit shift envelope} is
\begin{equation}
\begin{split}
 \widehat{\mathcal E}_e=\{(\boldsymbol\gamma,\boldsymbol\eta):
 &U^T_{e,g}(\gamma_g)\leq\tau\quad\forall g,\\
 &\tfrac12\textstyle\sum_s U^L_{e,a,s}(\eta_s)\leq\lambda
 \quad\forall a\}.
 \label{eq:envelope}
\end{split}
\end{equation}
Profiles that place deployment mass on an unobserved required environment are
excluded. A missing source class excludes balanced-leakage certification
unless a structural assumption identifies its conditional recall.

\begin{theorem}[Support-aware representation-edit shift envelope]
\label{thm:shift-envelope}
With probability at least $1-\delta$, simultaneously for every registered edit
$e$, every deployment profile in its certified envelope satisfies every
registered target and balanced-leakage contract. Environment mixture weights
and source-class prevalences may be chosen arbitrarily after certification.
Profiles may also be chosen after inspecting the envelope without another
multiplicity correction. A required target environment or source class with
zero certification observations is excluded rather than extrapolated.
\end{theorem}

\begin{proof}
The simultaneous event used for the individual curves already ranges over
every edit, target environment, source class, and attacker, and each curve is
valid for every value of its density-ratio argument. On that event, membership
in Eq.~\eqref{eq:envelope} controls target harm for every allowed $Q_g$ and
balanced leakage for every allowed $Q_s$. Arbitrary environment mixing
preserves the target threshold by Corollary~\ref{cor:mixture}; source prevalence
does not enter Eq.~\eqref{eq:balanced-leakage}. Inspecting or intersecting
objects valid on this same event does not spend additional error probability.
An unobserved required conditional law has no confidence curve and therefore
contributes no admissible envelope coordinate.
\end{proof}

\begin{corollary}[Common radius and post-certification profile choice]
\label{cor:common-radius}
Under Theorem~\ref{thm:shift-envelope}, the largest certified common budget is
\begin{equation}
 \widehat\Gamma_e=\sup\{\Gamma\geq1:
 (\Gamma\mathbf 1_{|\mathcal G|},\Gamma,\Gamma)
 \in\widehat{\mathcal E}_e\},
\end{equation}
with value zero if the IID profile fails. No additional multiplicity
correction is required to inspect the envelope or choose a contained profile
after certification.
\end{corollary}

\begin{proof}
Restrict Theorem~\ref{thm:shift-envelope} to the diagonal profile. Both the
diagonal supremum and any later anisotropic profile choice are functions of the
same simultaneous confidence event.
\end{proof}

\begin{corollary}[False acceptance]
Under the conditions of Theorem~\ref{thm:robust-paired}, the probability that
VERA accepts an edit violating at least one declared robust contract is at most
$\delta$.
\end{corollary}

For edit $e$, let $\mathcal{K}_e$ index its paired target-harm and registered
leakage contracts, with thresholds $c_k$. Define the population representation-edit shift
radius
\begin{equation}
 \Gamma_e^\star=\sup\{\Gamma\geq1:
 \rho_{\Gamma,P_k}(V_k)\leq c_k\ \text{for every }k\in\mathcal{K}_e\},
\end{equation}
with $\Gamma_e^\star=0$ when a contract fails at $\Gamma=1$. Let
$\widehat\Gamma_e$ replace each population robust risk by the upper bound in
Theorem~\ref{thm:robust-paired}, and use the same zero convention.

\begin{theorem}[Certified representation-edit shift radius]
\label{thm:shift-radius}
With probability at least $1-\delta$, simultaneously for every registered edit
$e$, $\widehat\Gamma_e\leq\Gamma_e^\star$. The statement holds uniformly over
the continuum of $\Gamma\geq1$; consequently, a user may select any deployment
budget $\Gamma\leq\widehat\Gamma_e$ after observing the certificate without an
additional multiplicity correction. If computation is capped at
$\Gamma_{\max}$, equality $\widehat\Gamma_e=\Gamma_{\max}$ is reported as
right-censored.
\end{theorem}

\begin{proof}
The DKW event in Theorem~\ref{thm:robust-paired} does not depend on $\Gamma$.
On that event, for every $k$ and every $\Gamma\geq1$, the reported upper curve
dominates $\rho_{\Gamma,P_k}(V_k)$. Hence every $\Gamma$ admitted by all
empirical upper curves is admitted by all population contracts. Taking the
supremum proves $\widehat\Gamma_e\leq\Gamma_e^\star$ for every edit on the same
simultaneous event. Robust risk is nondecreasing in $\Gamma$ because the
ambiguity sets are nested, so the feasible budgets form an interval and
bisection is valid. Post-certificate choice within that interval leaves the
event unchanged.
\end{proof}

\begin{theorem}[Sufficient certification sample size]
\label{thm:sample-complexity-upper}
Fix a component with range length $R=b-a$, declared budget $\Gamma_0$, and
threshold $c$. Construct its DKW upper curve with component undercoverage
probability $\alpha$. If its population robust risk obeys
$\rho_{\Gamma_0,P}(V)\leq c-m$ for margin $m>0$, then
\begin{equation}
 n\geq \frac{\Gamma_0^2R^2}{2m^2}
 \left(\sqrt{\log\frac{2}{\alpha}}+
       \sqrt{\log\frac{2J}{\beta}}\right)^2
 \label{eq:sample-complexity-upper}
\end{equation}
is sufficient for that component to pass with probability at least
$1-\beta/J$. Consequently, if all $J$ components of a fixed candidate have
positive margins and satisfy Eq.~\eqref{eq:sample-complexity-upper}, the
candidate passes every component with probability at least $1-\beta$.
For an envelope, any $\Gamma_0>1$ satisfying these margins yields a nontrivial
certified coordinate with the same probability. Exact discrete intervals can
improve this sufficient bound but do not weaken it.
\end{theorem}

\begin{proof}
Besides the coverage penalty built into the reported upper curve, a second DKW
event at error $\beta/J$ gives
$\widehat\rho_{\Gamma_0,n}(V)\leq
\rho_{\Gamma_0,P}(V)+\Gamma_0R
\sqrt{\log(2J/\beta)/(2n)}$.
Thus the reported upper bound is at most $c$ whenever the sum of this sampling
term and the built-in term
$\Gamma_0R\sqrt{\log(2/\alpha)/(2n)}$ is at most $m$.
Solving gives Eq.~\eqref{eq:sample-complexity-upper}; a union bound over the
$J$ power events proves the joint statement.
\end{proof}

\begin{corollary}[Minimax prospective evidence allocation]
\label{cor:evidence-allocation}
Fix $J$ components with range lengths $R_j$, declared budgets $\Gamma_j$,
positive margins $m_j$, and component undercoverage probabilities $\alpha_j$.
For joint power $1-\beta$, define the sufficient evidence scores
\begin{equation}
 A_j=\frac{\Gamma_j^2R_j^2}{2m_j^2}
 \left(\sqrt{\log\frac{2}{\alpha_j}}+
       \sqrt{\log\frac{2J}{\beta}}\right)^2.
 \label{eq:evidence-score}
\end{equation}
Prospective counts $n_j\geq A_j$ for every component are sufficient for all
components to pass with probability at least $1-\beta$. More generally, among
positive real allocations with $\sum_j n_j=N$, the allocation minimizing the
largest normalized evidence deficit $\max_j A_j/n_j$ is
\begin{equation}
 n_j^\star=N\frac{A_j}{\sum_{\ell=1}^J A_\ell},
 \qquad
 \min_{\boldsymbol n}\max_j\frac{A_j}{n_j}
 =\frac{\sum_j A_j}{N}.
 \label{eq:minimax-allocation}
\end{equation}
Thus, when confidence factors and ranges are shared, the minimax
sufficient-evidence score is proportional to $\Gamma_j^2/m_j^2$. Replacing
unknown margins by estimates from
an independent design fold, imposing prespecified evidence floors, and rounding
to integer counts can change power but not certification validity: conditional
on the design fold, the allocation remains fixed before certification.
If one sampled evidence cell informs several components, replace its score by
the maximum $A_j$ among components sharing that cell and allocate over cells.
Meeting the cellwise maxima meets every componentwise sufficient condition, and
the same minimax argument applies to these aggregated scores.
\end{corollary}

\begin{proof}
The joint sufficient condition follows by applying
Theorem~\ref{thm:sample-complexity-upper} to each component and union bounding
the $J$ power events. For any allocation, if
$r=\max_j A_j/n_j$, then $A_j\leq r n_j$ for every $j$, so
$\sum_j A_j\leq rN$. Hence $r\geq\sum_j A_j/N$. The displayed allocation makes
every ratio $A_j/n_j$ equal to this lower bound. Conditional validity under a
design-dependent allocation follows from the probability-space contract in
Theorem~\ref{thm:robust-paired}; averaging the conditional guarantee gives the
same unconditional guarantee.
\end{proof}

Corollary~\ref{cor:evidence-allocation} treats each contract as depending on one
evidence cell. Balanced leakage is additive across two source-class cells, and
one source-class sample can simultaneously evaluate several attackers. The next
result handles both directions of sharing.

\begin{theorem}[Additive multi-cell evidence allocation]
\label{thm:additive-allocation}
Let $c=1,\ldots,C$ index independently sampled evidence cells and
$j=1,\ldots,J$ index contracts. Contract $j$ has nonnegative weights $w_{jc}$,
population risk
\begin{equation}
 R_j=\sum_{c=1}^C w_{jc}\rho_{\Gamma_{jc},P_{jc}}(V_{jc}),
 \qquad R_j\leq q_j-m_j,
 \label{eq:additive-contract}
\end{equation}
where $m_j>0$, $V_{jc}$ has range length $R_{jc}$, and terms with
$w_{jc}=0$ are omitted. Samples inside a cell may be reused across contracts and
need not produce independent audit variables. Let $D$ be the number of distinct
nonzero cell-risk curves, assign each distinct curve one DKW undercoverage
probability $\alpha_{jc}$ (shared wherever that curve is reused), require the
sum of those $D$ distinct-curve probabilities to be at most the global
certification error budget $\delta$, and define
\begin{equation}
 b_{jc}=\frac{w_{jc}\Gamma_{jc}R_{jc}}{\sqrt{2}}
 \left(
   \sqrt{\log\frac{2}{\alpha_{jc}}}
   +\sqrt{\log\frac{2D}{\beta}}
 \right).
 \label{eq:additive-coefficient}
\end{equation}
If prospective cell counts satisfy
\begin{equation}
 \sum_{c=1}^C\frac{b_{jc}}{\sqrt{n_c}}\leq m_j
 \quad\text{for every }j,
 \label{eq:additive-power-condition}
\end{equation}
then every contract passes its additive DKW upper bound with probability at
least $1-\beta$.

For any positive design-fold margins $\widetilde m_j$, put
$a_{jc}=b_{jc}/\widetilde m_j$. Given budget $N$ and positive floors $\ell_c$
with $N\geq\sum_c\ell_c$,
the prospective surrogate allocation is the convex program
\begin{equation}
 \begin{aligned}
  \underset{\boldsymbol n,t}{\operatorname{minimize}}\quad &t\\
  \text{subject to}\quad
  &\sum_c a_{jc}n_c^{-1/2}\leq t &&\forall j,\\
  &\sum_c n_c=N,\qquad n_c\geq\ell_c &&\forall c.
 \end{aligned}
 \label{eq:additive-allocation}
\end{equation}
It exactly minimizes the worst normalized additive DKW slack for the fixed
design-fold coefficients. With one contract and inactive floors, its solution is
\begin{equation}
 n_c^\star=N\frac{a_{1c}^{2/3}}{\sum_d a_{1d}^{2/3}},
 \qquad
 \min_{\boldsymbol n}\sum_c\frac{a_{1c}}{\sqrt{n_c}}
 =\frac{(\sum_c a_{1c}^{2/3})^{3/2}}{\sqrt N}.
 \label{eq:additive-single-contract}
\end{equation}
If every contract depends on exactly one cell, every optimized cell appears in
at least one contract, and the floors are inactive, define
$\bar a_c=\max_{j:w_{jc}>0}a_{jc}$. Then
$n_c^\star=N\bar a_c^2/\sum_d\bar a_d^2$, recovering the shared-cell
square-score allocation in Corollary~\ref{cor:evidence-allocation}. Design-fold
margin substitution, floors, and deterministic integer rounding can change
power and exact optimality after rounding, but not certification validity.
\end{theorem}

\begin{proof}
For every distinct nonzero cell-risk curve represented by a pair $(j,c)$, the
DKW coverage penalty contributes
\begin{equation*}
w_{jc}\Gamma_{jc}R_{jc}
\sqrt{\frac{\log(2/\alpha_{jc})}{2n_c}}
\end{equation*}
to the reported additive upper bound. A second
DKW event at error $\beta/D$ upper-bounds the corresponding empirical robust
risk above its population value by
\begin{equation*}
\Gamma_{jc}R_{jc}\sqrt{\frac{\log(2D/\beta)}{2n_c}}.
\end{equation*}
A union bound over the $D$
power events is valid despite shared samples or dependent audit variables. On
their intersection, the reported bound for contract $j$ is at most
$R_j+\sum_cb_{jc}/\sqrt{n_c}$, which is no greater than $q_j$ under
Eq.~\eqref{eq:additive-power-condition}.
The distinct-curve $\alpha$ budget separately makes all reported additive
upper bounds valid with probability at least $1-\delta$; reuse of one curve
across contracts spends its undercoverage probability only once.

For fixed positive coefficients, $n\mapsto n^{-1/2}$ is convex on
$(0,\infty)$. Each contract constraint in Eq.~\eqref{eq:additive-allocation} is
therefore convex, and the budget and floor constraints are affine. The epigraph
program exactly represents the maximum normalized slack and attains a minimizer
on its compact feasible set. With one contract and inactive floors, the
Lagrange stationarity condition is
$-a_{1c}/(2n_c^{3/2})+\nu=0$, so $n_c\propto a_{1c}^{2/3}$; normalizing by $N$
and substituting gives Eq.~\eqref{eq:additive-single-contract}. If contract $j$
uses only cell $c(j)$ and every cell is represented, the objective is
$\max_c\bar a_c/\sqrt{n_c}$. Squaring it gives the normalized deficit problem
with scores $\bar a_c^2$, so Corollary~\ref{cor:evidence-allocation} yields the
last formula when the floors are inactive. Conditioning on the independent
design fold fixes all allocation
choices before certification; validity follows from the same conditional
probability argument used above.
\end{proof}

\begin{theorem}[Prospective multi-component lower bound]
\label{thm:sample-complexity-lower}
For $j=1,\ldots,J$, choose $0<p_{0j}<p_{1j}<1$ such that
$\Gamma_jp_{1j}\leq1$, $\Gamma_jp_{0j}\leq c_j$, and
$\Gamma_jp_{1j}>c_j$. A prospective protocol observes $n_j$ independent
Bernoulli samples from each component. Let $P_0$ denote the world in which all
components have parameters $p_{0j}$, and let $P_j$ differ only by replacing
$p_{0j}$ with $p_{1j}$. If a possibly randomized protocol accepts with
probability at least $1-\beta$ under $P_0$ and falsely accepts with probability
at most $\alpha$ under every $P_j$, where $\alpha+\beta<1/2$, then
\begin{equation}
 n_j\geq
 \frac{\log\{1/[2(\alpha+\beta)]\}}
 {d_{\mathrm{KL}}(\mathrm{Bern}(p_{0j})\Vert
                  \mathrm{Bern}(p_{1j}))}
 \quad\text{for every }j.
 \label{eq:sample-complexity-lower}
\end{equation}
Consequently, the total evidence $N=\sum_jn_j$ is at least the sum of these
bounds. Fix $\kappa\in(0,1/2)$. Taking
$p_{0j}=(c_j-m_j)/\Gamma_j$ and
$p_{1j}=(c_j+m_j)/\Gamma_j$ in a compact interior regime where both
probabilities lie in $[\kappa,1-\kappa]$ requires
\begin{equation}
 N=\Omega\left(
 \log\frac{1}{\alpha+\beta}
 \sum_{j=1}^J\frac{\Gamma_j^2}{m_j^2}
 \right).
\end{equation}
Thus, locally in such compact interior regimes, the quadratic shift-budget and
inverse-margin allocation in Corollary~\ref{cor:evidence-allocation} is
unavoidable up to confidence and $\kappa$-dependent constants for prospective
independent-cell designs. This scaling statement is not uniform as probabilities
approach zero or one; the exact KL bound above remains the global statement.
\end{theorem}

\begin{proof}
Let $A$ be the event that the protocol accepts. The two testing errors satisfy
$P_0(A^c)\leq\beta$ and $P_j(A)\leq\alpha$. The
Bretagnolle--Huber inequality applied to $P_0$ and $P_j$ gives
\begin{equation}
 P_0(A^c)+P_j(A)
 \geq\tfrac12\exp\{-n_j\,d_{\mathrm{KL}}(p_{0j}\Vert p_{1j})\},
\end{equation}
because the two product laws differ in only the $n_j$ observations from
component $j$. Rearranging proves Eq.~\eqref{eq:sample-complexity-lower} for
every $j$, and summing gives the total lower bound. On
$[\kappa,1-\kappa]$, Bernoulli KL is bounded above by a
$\kappa$-dependent constant times
$(p_{1j}-p_{0j})^2=(2m_j/\Gamma_j)^2$, proving the stated local order. Near the
boundary, that uniform quadratic comparison need not hold, which is why the
theorem retains the exact KL denominator.
\end{proof}

\begin{theorem}[Unsupported-cell impossibility]
\label{thm:unsupported}
Fix an edit $e$, a contract threshold $c$, and let $O_n$ contain every random
quantity available to a certification-data-only protocol. Suppose an audit cell
$A$ has zero certification probability, the allowed deployment class contains a
law $Q_A$ supported on $A$, and the nonparametric model class contains two
worlds $M_0,M_1$ such that
\begin{enumerate}
  \item $O_n$ has the same distribution under $M_0$ and $M_1$;
  \item $\mathbb{E}_{Q_A,M_0}[V_e]\leq c$; and
  \item $\mathbb{E}_{Q_A,M_1}[V_e]>c$.
\end{enumerate}
If a possibly randomized protocol controls false acceptance at level $\delta$
uniformly over this model and deployment class, then its probability of
accepting $e$ under the safe world $M_0$ is at most $\delta$.
\end{theorem}

\begin{proof}
Include the protocol's independent random seed in $O_n$. By condition 1, its
acceptance probability $p$ is identical in the two worlds. Under $M_1$ and
$Q_A$, acceptance of $e$ is a false acceptance by condition 3. Uniform control
therefore requires $p\leq\delta$. The same bound holds under $M_0$, although
condition 2 says that $e$ is safe there. Equivalently, the two observable
experiments have total-variation distance zero, so no test can distinguish
them.
\end{proof}

An audit cell may be an input region, an environment, or an
environment--source-label pair. Thus the result covers both an absent
deployment environment and a conditional leakage contract whose required
label cell is unobserved. A single-class slice cannot identify the omitted
class's conditional leakage without a structural assumption. In the
preregistered Camelyon17 split, official hospital center 2 occurs only in the
external split, whereas centers 0, 1, 3, and 4 are observed during
certification; moreover, the binary center-0 source label is constant in the
center-2 external slice. A uniform certificate over the missing cells must
acquire representative support, assert a testable cross-cell model, or abstain.
The dataset instantiates the support boundary; it is not evidence for the
theorem by itself.
